---
title: "My Fancy Presentation"
author: "Nikhil"
date: "June 15, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## My new slide
```{r, comment = "", echo = TRUE}

head(mtcars)

```

## My new slide 2
```{r, comment = "", fig.align='center',fig.cap='My Awesome Figure'}

plot(mtcars$wt, mtcars$mpg,xlab ="Weight", ylab = "MPG")

```

## New page with title

### Top level sub heading
#### Second level sub heading


- Bullet 1
- Bullet 2

1. Item a
2. Item b


***
Page without title

Plain text

*italicized text*

**Bold text**

`for(int %in% 1:10)`

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

