---
title: "Presentation and Plotly - Week 3 Assignment"
author: "Nikhil"
date: "June 16, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##USEPA Environmental Quality Index (EQI)


- *Data Source*: https://catalog.data.gov/dataset/usepa-environmental-quality-index-eqi-air-water-land-built-and-sociodemographic-domains-transf

- *Metadata*: https://catalog.data.gov/harvest/object/c668b067-46a2-4a12-a541-c8c960d75f65/html/original

The following slides show:


- Distribution of air, water and metal pollutants by state
- Interrelation between air, water and metal pollutants by state with color coded categories

***
```{r,cache=TRUE}

#Metadata: 
eqidata <- read.csv("https://edg.epa.gov/data/Public/ORD/NHEERL/EQI/Eqidata_all_domains_2014March11.csv")

```

```{r,warning=FALSE,message=FALSE}
library(plotly)
library(dplyr)
summarized_data <- eqidata %>% tbl_df() %>%
mutate(
air_data = rowSums(eqidata[, 6:92]),
water_data = rowSums(eqidata[, 105:165]),
metal_data = rowSums(eqidata[, 175:187])
) %>%
group_by(state_name, cat_rucc) %>%
summarize(
air_data = sum(air_data),
water_data = sum(water_data),
metal_data = sum(metal_data),
numdays_rain_activity_tot = sum(numdays_rain_activity_tot),
county_pop_2000 = sum(county_pop_2000)
)

```


## Plotly Graph - Population vs Air Pollutants Data 
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ county_pop_2000,
  y =  ~ air_data,
  type = "scatter",
  mode = "markers",
  color = ~ cat_rucc
  ) %>% layout(xaxis = list(title = "Population"),
  yaxis = list(title = "Air Pollutants"))
```

## Plotly Graph - Population vs Water Pollutants Data
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ county_pop_2000,
  y =  ~ water_data,
  type = "scatter",
  mode = "markers",
  color = ~ cat_rucc
  ) %>% layout(xaxis = list(title = "Population"),
  yaxis = list(title = "Water Pollutants"))

```

## Plotly Graph - Population vs Metal Pollutants Data
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ county_pop_2000,
  y =  ~ metal_data,
  type = "scatter",
  mode = "markers",
  color = ~ cat_rucc
  ) %>% layout(xaxis = list(title = "Population"),
  yaxis = list(title = "Metal Pollutants"))

```


## Plotly Graph - Water Pollutants vs Air Pollutants Data
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ water_data,
  y =  ~ air_data,
  type = "scatter",
  mode = "markers",
  color = ~ cat_rucc
  ) %>% layout(
  xaxis = list(title = "Water Pollutants"),
  yaxis = list(title = "Air Pollutants")
  )
```

## Plotly Graph - Water Pollutants vs Metal Pollutants Data
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ water_data,
  y =  ~ metal_data,
  type = "scatter",
  mode = "markers",
  color = ~ cat_rucc
  ) %>% layout(
  xaxis = list(title = "Water Pollutants"),
  yaxis = list(title = "Metal Pollutants")
  )
```

## Plotly Graph - Metal Pollutants vs Air Pollutants Data
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ metal_data,
  y =  ~ air_data,
  type = "scatter",
  mode = "markers",
  color = ~ cat_rucc
  ) %>% layout(
  xaxis = list(title = "Metal Pollutants"),
  yaxis = list(title = "Air Pollutants")
  )
```


## Plotly Graph - State vs Number of Rain Activity Days
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ state_name,
  y =  ~ numdays_rain_activity_tot,
  type = "bar"
  ) %>% layout(
  xaxis = list(title = "US States"),
  yaxis = list(title = "Number of days of Rain Activity")
  )
```

## Plotly Graph - State vs Population
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ state_name,
  y =  ~ county_pop_2000,
  type = "bar"
  ) %>% layout(xaxis = list(title = "US States"),
  yaxis = list(title = "Population"))
```

## Plotly Graph - State vs Air Pollutants Data
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ state_name,
  y =  ~ air_data,
  type = "bar"
  ) %>% layout(xaxis = list(title = "US States"),
  yaxis = list(title = "Air Pollutants"))
```

## Plotly Graph - State vs Water Pollutants Data
```{r,warning=FALSE,message=FALSE}
plot_ly(
  summarized_data,
  x =  ~ state_name,
  y =  ~ water_data,
  type = "bar"
  ) %>% layout(xaxis = list(title = "US States"),
  yaxis = list(title = "Water Pollutants"))
```

